Recursive Neural Network Part-of-Speech Tagger

### 2013-12-21 paper/paper.tex
Describe experimental setup. Describe training tricks. Fix some transition words.

Finally, each $p_j$ is passed along to the classifier, which applies the operation:

@@

TODO: Describe experiments.

@@

TODO: Describe training tricks.

>>>>

Subsequently, each $p_j$ is passed along to the classifier, which applies the operation:

@@

Our experiments consisted of training the recursive network on training sentences drawn from the Penn Treebank data of assignment three, as we described above. We frequently trained on 100, 1000, 10,000 or 39,815 (all) of the training sentences in exploring the performance of the recursive neural network for part-of-speech tagging. Training on the entire data set for 25 iterations, or on 10,000 training sentences for 100 iterations, each took about 4 hours on a 2012 Macbook Pro Retina with a 2.6 GHz Intel Core i7 CPU and 8 GB of RAM.

To evaluate the network, we used a basic metric which counts the ratio of the number of correctly tagged words out of the total number of words within the validation or test set (1700 in-domain validation sentences, 1016 out-of-domain validation sentences and 1015 out-of-domain test sentences). We also count the ratio of correctly tagged unknown words, where a word is defined to be unknown if it was not encountered during the training set; however, note that it may be present within $\mathcal{V}$, the vocabulary associated with the distributed representation lookup table. If the word is unknown to the distributed representation lookup table, the model falls back upon the distributed representation for the special token ``UNKNOWN."

@@

Training neural networks can be tricky since the backpropagation algorithm relies upon a learning rate parameter as well as initial weight and bias values. The learning rate should not be too large, otherwise the gradient descent will skip over local or global minima. However, it should also not be too small, otherwise training may take too long. It perhaps should vary over the course of training and decrease in order to better fine tune the fit to the minima. However, it's not obvious exactly which set of choices will be best.

We researched existing techniques to choose initial weights and biases, and to better update the weights based on adaptive learning rates, as described in the next subsections.
